\hrule\hrule\bigskip\bigskip A simple and efficient algorithm for computing approximate Nash equilibria in two-person zero-sum games with imcomplete information

### 2015-06-07 nips2015.tex
more ENHs on algo tex

The idea is to replace the usual necessary condition ``$0 \in \partial
f(x)$'' for the optimality of $x$ with ``$v \in \partial_\epsilon
f(x)$, for some small perturbation vector $v$''. In fact, it is easy
to see that, for each $x \in X$, $(\partial_\epsilon f(x))_{\epsilon >
  0}$ is a decreasing sequence of sets which converges to $\partial
f(x)$.

Henceforth, the notion of approximate Nash equilibria will be
understood in the following sense, which was first introduced in
\cite{he2013accelerating}.

%% Since won't typically be able to compute a feasible point in $Q_1 \in
%% Q_2$ (due to the equality constraints $E_kz = e_k$), we will consider
%% an approximate equilibrium concept which takes in to account the
%% distance from the set of equilibria. Viz,

\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
Given $\rho > 0$ and $\epsilon > 0$, a Nash
$(\rho,\epsilon$)-equilibrium is a pair $(x^*, y^*)$ of realization
plans such that there exists dual vectors $p^*$ and $q^*$ and a
pertubation vector $v^*$ for which
\begin{eqnarray}
\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
\end{eqnarray}
\label{thm:cool_notion}
\end{definition}

@@

%\paragraph{\textbf{Plan of attack.}}
\textbf{XXX TODO: Define the ergodic variables $\tilde{v}^a$ and
  $\tilde{\epsilon}^a$, ...}

\subsection{The algorithm proper and its convergence rate}
Consider the following algorithm for solving the GSP
\eqref{eq:unconstrained_pb}
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$(\tilde{y},\tilde{p},\tilde{x},\tilde{q}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$,
%% $y^{(0)} \leftarrow 0_{n_2}$,
%% $p^{(0)} \leftarrow 0_{l_1}$, $x^{(0)} \leftarrow 0_{n_1}$, $q^{(0)}
%% \leftarrow 0_{l_2}$,
$k \leftarrow 0$
\While{$\|\tilde{\epsilon}^{a}_k\| \ge \rho$ or $\|\tilde{v}^{a}_k\| \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
\lambda(E_2y^{(k+1)}-e_2)$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1(x^{(k+1)}-x^{(k)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
Let $d_0$ be the euclidean distance between the starting point
$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
Then given any $\epsilon > 0$ and $\rho > 0$, we have the ergodic
error bounds
\begin{eqnarray}
\|\tilde{\epsilon}^{a}_k\| \le \rho\text{ and }\|\tilde{v}^{a}_k\| \le
\epsilon, \forall k \ge 2d_0\|K\|max(5d_0/\rho, 1/\epsilon).
\end{eqnarray}

>>>>

The idea behind $\epsilon$-subgradients is the following: given a
function $f$ which we wish to minimize, replace the usual necessary
condition ``$0 \in \partial f(x)$'' for the optimality of $x$ with the
weaker condition ``$\exists v \in \partial_\epsilon f(x)$, for some small
perturbation vector $v$''. In fact, it is easy to see that, for each
$x \in X$, $(\partial_\epsilon f(x))_{\epsilon > 0}$ is a decreasing
sequence of sets which converges to $\partial f(x)$.

This approximation concept for subgradients yields the following
concept of approximate Nash equlibria (adapted from
\cite{he2013accelerating}).

\begin{definition}[\textbf{Nash $(\rho,\epsilon)$-equilibria}]
Given $\rho > 0$ and $\epsilon > 0$, a Nash
$(\rho,\epsilon$)-equilibrium for the GSP \eqref{eq:unconstrained_pb}
is any quadruplet $(x^*, y^*, x^*, q^*)$ for which
there exists a perturbation vector $v^*$ such that
\begin{eqnarray}
\|v^*\| \le \rho \text{ and}\hspace{.5em} v^* \in
\partial_\epsilon[\hat{\Psi}_1(., ., x^*, q^*) +
  \hat{\Psi}_2(y^*, p^*, , .)](y^*,p^*,x^*,q^*).
\end{eqnarray}

Such a vector $v^*$ is called a Nash $\epsilon$-residual at $(x^*,
y^*, x^*, q^*)$.
\label{thm:cool_notion}
\end{definition}

@@

\subsection{The algorithm proper and its convergence rate}
Consider the following algorithm for solving the GSP
\eqref{eq:unconstrained_pb}
\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\rho >0$, $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\rho, \epsilon)$-equilibrium
$(\tilde{y},\tilde{p},\tilde{x},\tilde{q}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$,
$\tilde{v}_a^{(0)} \leftarrow 0$, $k \leftarrow 0$
\While{$\|\tilde{\epsilon}_a^{(k)}\| \ge \rho$ or
  $\|\tilde{v}_{a}^{(k)}\| \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$
\State  \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$
\State  \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} +
\lambda(E_2y^{(k+1)}-e_2)$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda
(A^T(x^{(k+1)}-x^{(k)}) + E_2^T(q^{(k+1)}-q^{(k)}))$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda
E_1(x^{(k+1)}-x^{(k)})$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k} +
\frac{1}{\lambda}(y^{(k+1)}-y^{(k)},p^{(k+1)}-p^{(k)},x^{(k+1)}-x^{(k)},q^{(k+1)}-q^{(k)})$
\State $\tilde{v}_a^{(k+1)} \leftarrow \frac{1}{k + 1}v_a^{(k+1)}$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Ergodic $\mathcal{O}(1/k)$ convergence]
Let $d_0$ be the euclidean distance between the starting point
$(y^{(0)},p^{(0)},x^{(0)},q^{(0)})$ of Algorithm \ref{Tab:algo} and the
set of equilibria for the GSP \eqref{eq:unconstrained_pb}.
Then given any $\epsilon > 0$ and $\rho > 0$, there exists and index
$k_0 \le 2d_0\|K\|max(5d_0/\rho, 1/\epsilon)$ such that the following
error bounds hold:
\begin{eqnarray}
\|\tilde{\epsilon}^{a}_{k_0}\| \le \rho\text{ and }\|\tilde{v}^{a}_{k_0}\| \le
\epsilon.
\end{eqnarray}
